Allowing Stable Groups of Prosumers to Enter the Market through Proper Aggregation

### 2014-09-12 Article.tex
update

In a smart grid environment, we study coalitions formation of prosumers that aim at selling energy to the grid. It is paramount for the grid operation that the energy producers are able to sustain the grid demand in term of stability and minimum production requirement in order to enter the energy market. We design an algorithm that seeks to form coalitions that will meet both of these requirements:  a minium energy level for the coalition and a production of an uncorrelated source of energy in order to have stable production level during the course of the bidding. We proposed an algorithm that uses graph tools such as correlation graphs or clique percolation to form coalition that meet such complex constraints. We validate the algorithm against a random procedure and show that, it not only performs better in term of social welfare for the power grid, but also that it is more robust against unforeseen production variations to due to changing weather condition for instance.

@@

In more details, and as will be explained in section \ref{sec:model}, we consider agents that, depending on meteorological conditions, personal preferences, and their appliances (loads and generators), consume and produce more or less energy (using only wind turbines and PV as generators, which can be quite simply and efficiently modeled).  We used real meteorological traces (see section \ref{sec:model}) to account for seasonal and daily variations in the prosumers energetic output profiles as well as realistic geographical correlations. With these ingredients, we are able simulate the different production/consumption profiles.

In section \ref{sec:forming} As correlations play a significant role in our mechanism, we organize the prosumers in a correlation graph, a quite popular approach in market stocks clustering since \cite{Mantegna1999} (see section \ref{sec:related}). We will see that in such graphs, cliques represent structures of interest. In our settings, it means that cliques are “good” (from the utility point of view) foundations for high valued coalitions. We thereby use a modified clique percolation algorithm (see section \ref{sec:results}) that will enable us to expand the cliques as much as needed in order to form proper coalitions that fulfill grid requirements. Finally, in section \ref{sec:results} provides some results.

@@

\section{Coalitions Formation}
\label{sec:forming}

>>>>

In a smart grid environment, we study coalitions formation of prosumers that aim at selling energy to the grid. It is paramount for the grid operation that the energy producers are able to sustain the grid requirements in term of stability and minimum production requirement in order to enter the energy market. We design an algorithm that seeks to form coalitions that will meet both of these requirements:  a minium energy level for the coalition and a production of an uncorrelated source of energy in order to have stable production level during the course of the bidding. We proposed an algorithm that uses graph tools such as correlation graphs or clique percolation to form coalition that meet such complex constraints. We validate the algorithm against a random procedure and show that, it not only performs better in term of social welfare for the power grid, but also that it is more robust against unforeseen production variations to due to changing weather condition for instance.

@@

In more details, and as will be explained in section \ref{sec:model}, we consider agents that, depending on meteorological conditions, personal preferences, and their appliances (loads and generators), consume and produce more or less energy (using only wind turbines and PV as generators, which can be quite simply and efficiently modeled).  We used real meteorological traces (see section \ref{sec:model}) to account for seasonal and daily variations in the prosumers energetic output profiles as well as realistic correlations. With these ingredients, we are able to run simulations and record the different output profiles as timeseries.

As correlations play a significant role in our mechanism, we organize the prosumers in a correlation graph, a quite popular approach in market stocks clustering since \cite{Mantegna1999} (see section \ref{sec:related}). We will see that in such graphs, cliques represent structures of interest. In our settings, it means that cliques are “good” (from the utility point of view) foundations for high valued coalitions. We thereby use a modified clique percolation algorithm (see section \ref{sec:results}) that will enable us to expand the cliques as much as needed in order to form proper coalitions that fulfill grid requirements.

The rest of the paper is organized as follows, section \ref{sec:related} locates our work in the related litterature. Section \ref{sec:model} explains the model we used to obtain realistic prosumers available power timeseries and introduces some notations. Section \ref{sec:forming} relates the method for building coalitions based on the agent timeseries. Finally, section \ref{sec:results} provides some results.

@@

\section{Forming coalitions}
\label{sec:forming}
